### 2023-11-06 manuscript/additional_files.Rmd
add the standards mix to additional files 4-6

Additional file 5.csv Table S8 -
The *m/z* features directly matched to predicted ionisation products of the spiked chemical compounds in urine.

Additional file 6.csv Table S9 -
The *m/z* features assigned to spiked chemical compounds in urine.

>>>>

Additional file 5.csv Table S8 -
The *m/z* features directly matched to theoretical ionisation products of the chemical standards in the standards mixed and spiked urine.

Additional file 6.csv Table S9 -
The *m/z* features assigned to chemical standards in the standards mix and spiked urine.
